Mobility Boomerang Plots

### 2020-07-21 notebooks/embedding_boomerang_plots.rmd
other small tweaks to figure

```{r}
plot <- df %>%
  mutate(
    highlight = ifelse(country %in% c("China", "United States", "Germany"), country, "Other"),
    highlight = factor(highlight, levels = c("United States", "China", "Germany", "Other"))
  ) %>%
  ggplot(aes(x = size, y = `l2-norm`, label = name, alpha = highlight, shape = highlight, color = highlight)) +
  geom_point(alpha = 0.5) +
  stat_smooth(
    method = "loess",
    se = F
  ) +
  scale_shape_manual(values = c(16, 16, 16, 16, 16,  1)) +
  scale_color_manual(values = c("#66c2a5", "#fc8d62", "#8da0cb", "#e78ac3", "#a6d854", "grey")) +
  scale_alpha_manual(values = c(1, 1, 1, 1, 1,  0.6)) +
  scale_x_log10(
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  ) +
  scale_y_continuous(
    limits = c(0, 7),
    breaks = c(2, 4, 6)
  ) +
  guides(shape = F) +
  theme_minimal() +
  theme(
    text = element_text(family = "Helvetica", size = 12),
    axis.title.x = element_text(angle = 0, size = 14, face = "bold", vjust = 0.5),
    axis.title.x.top = element_text(angle = 0, size = 14, face = "bold", vjust = 0.5),
    axis.text.x.top = element_blank(),
    axis.title.y = element_text(angle = 90, size = 14, face = "bold"),
    axis.title.y.right = element_text(angle = 90, size = 14, face = "bold"),
    axis.text.y.right = element_blank(),
    legend.text = element_text(size = 10),
    legend.position = c(0.14, 0.82),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    legend.title = element_blank(),
    axis.line = element_line(color="black", size = 0.3),
    legend.box.background = element_rect(color="black", size=0.1, fill = "white")
  ) +
  annotation_logticks(sides = "b") +
  xlab("# Researchers") +
  ylab("L2 Norm")

>>>>

```{r}
plot <- df %>%
  mutate(
    highlight = ifelse(country %in% c("China", "United States", "Germany"), country, "Other"),
    highlight = factor(highlight, levels = c("United States", "China", "Germany", "Other"))
  ) %>%
  ggplot(aes(x = size, y = `l2-norm`, label = name, alpha = highlight, shape = highlight, color = highlight)) +
  geom_point(alpha = 0.5) +
  stat_smooth(
    method = "loess",
    size = 1.25,
    se = F
  ) +
  scale_shape_manual(values = c(16, 16, 16, 1)) +
  scale_color_manual(values = c("#66c2a5", "#fc8d62", "#8da0cb", "darkgrey")) +
  scale_fill_manual(values = c("#66c2a5", "#fc8d62", "#8da0cb", "grey")) +
  scale_alpha_manual(values = c(1, 1, 1,  0.6)) +
  scale_x_log10(
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  ) +
  scale_y_continuous(
    limits = c(0, 7),
    breaks = c(2, 4, 6)
  ) +
  guides(shape = F) +
  theme_minimal() +
  theme(
    text = element_text(family = "Helvetica", size = 12),
    axis.title.x = element_text(angle = 0, size = 14, face = "bold", vjust = 0.5),
    axis.title.x.top = element_text(angle = 0, size = 14, face = "bold", vjust = 0.5),
    axis.text.x.top = element_blank(),
    axis.title.y = element_text(angle = 90, size = 14, face = "bold"),
    axis.title.y.right = element_text(angle = 90, size = 14, face = "bold"),
    axis.text.y.right = element_blank(),
    legend.text = element_text(size = 10),
    legend.position = c(0.14, 0.82),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    legend.title = element_blank(),
    axis.line = element_line(color="black", size = 0.3),
    legend.box.background = element_rect(color="black", size=0.1, fill = "white")
  ) +
  annotation_logticks(sides = "b") +
  xlab("# Researchers") +
  ylab("L2 Norm")
